Plots

### 2025-06-18 manuscript/manuscript.tex
Remove we

Recently, Large Language Models (LLM), leveraging massive datasets and deep learning approaches, have made advances in performing a variety of Natural Language Processing (NLP) tasks using free-text, such as question answering, code generation, and even medical diagnosis \citep{changSurveyEvaluationLarge2023,lundChattingChatGPTHow2023,svyatkovskiyIntelliCodeComposeCode2020,hauptAIGeneratedMedicalAdvice2023}. In 2022, a widely-available LLM called ChatGPT was released by OpenAI with capabilities of answering natural language text inquiries using training data up to September 2021. ChatGPT-3 was based on several Generative Pre-trained Transformer (GPT) models between 2018 to 2020, namely GPT-1 to GPT-3, which had notable differences in training data sizes of 5 gigabytes to 45 terabytes from web sources that resulted in 117 million to 175 billion parameter models \citep{wuBriefOverviewChatGPT2023}. In March 2023, ChatGPT-4 was released with human-level performance on various professional and academic exams and benchmarks that outperformed ChatGPT-3 \citep{openaiGPT4TechnicalReport2023}. Given the limited usage of free-text open narratives in computer models for determining CODs, and recent advances in LLMs that leverage natural language text prompts, we conducted a study with Sierra Leone deaths from VA in 2019 to 2022 to compare four models, GPT-3.5, GPT-4, InterVA-5, and InSilicoVA, to physicians for determining CODs.

@@

Since computer models were compared to physicians in this study, there was more certainty that COD assignments agreed by both physicians were representative of physician assignment than when they disagreed \citep{barnettComparativeAccuracyDiagnosis2019,morrisFactorsAssociatedPhysician2010,hsiaoFactorsAssociatedPhysician2012}. Thus, we used 6942 physician agreed records of the 11,920 total records. For better comparison, we standardized all codes to CGHR-10 codes (see Additional File 1) that generalized ICD-10 codes into 19, 10, and 7 categories for the adult (12 to 69 years), child (28 days to 11 years), and neonatal (under 28 days) age groups. After conversion, a final total of 6939 physician agreed records (3826 adult, 2636 child, and 477 neonatal) were used for modelling and performance evaluation. See Appendix \ref{app-methods-data} for further details on data preprocessing and Tables \ref{tab-data-cod} and \ref{tab-data-age} for COD and age range distributions of the physician agreed records.

@@

Of all 6939 records, GPT-4 (0.61 PCCC) had the highest individual performance followed by GPT-3.5 (0.56 PCCC), InSilicoVA (0.44 PCCC), and InterVA-5 (0.44 PCCC) (Figure \ref{fig-pccc-csmf}). GPT-3.5 and GPT-4 had improvements ranging from 0.14-0.18 PCCC over InSilicoVA and InterVA-5, while GPT-4 slightly improved over GPT-3.5 by 0.05 PCCC. Population level performances were similar for all models (0.74-0.79 CSMF). Figure \ref{fig-pccc} shows the PCCC performance across three age groups (adult, child, and neonate). GPT-4 had the best individual performance for adult and neonatal records (0.64 and 0.58 PCCC), while GPT-3.5 had the best performance for child records (0.54 PCCC) with GPT-4 performing slightly worse (0.51 PCCC). InSilicoVA and InterVA-5 performed the worse for adult and child records ($\leq$0.5 PCCC), while GPT-3.5 performed the worse for neonatal records (0.42 PCCC). Across ages, all models followed a similar pattern in individual performance (Figure \ref{fig-pccc-age}). PCCC trended upwards for 1 month to 14 years ($\sim$0.1-0.75), and downwards for ages 15 to 69 years ($\sim$0.7-0.35). The highest and lowest performances were observed for ages 10-29 years ($\sim$) and 1-11 months respectively. Performances varied more across models for ages 0 days to 5 years, while less variation was seen between GPT-3.5 and GPT-4, as well as InSilicoVA and InterVA-5, from 5 to 69 years.

@@

GPT-3.5 and GPT-4 models used default parameters with the exception of setting the temperature to 0 for more consistent results. However, the temperature and other model settings may be adjusted to possibly improve performance for GPT models \citep{openaiOpenAIPlatformAPI2024}. This was not examined as sensitivity analyses on model parameters are costly across multiple reruns, noted in Section \ref{discuss-disadv-reprod}, which is required when testing various parameter settings. In addition, GPT models may possibly produce inconsistent results even with the temperature set to 0. Thus, it is important to also test the reliability and consistency of GPT outputs to avoid coincidental results due to randomness \citep{johnsonAssessingAccuracyReliability2023,jangConsistencyAnalysisChatGPT2023,krishnaEvaluationReliabilityRepeatability2024}. InterVA-5 and InSilicoVA were able to provide multiple COD assignments with probabilities for each COD. GPT models can be prompted to produce more than one COD assignment, but was not explored in this study as we only evaluated the most probable COD. This may be useful to evaluate the performance of multiple alternative COD assignments, which may provide additional diagnoses that have a higher chance of being similar to physician assignment, and better reflect causes leading to death \citep{solemanVerbalAutopsyCurrent2006}.

@@

Our study lays the foundation for the integration of GPT, InterVA-5, and InSilicoVA models into VA systems to assist physicians in COD assignment. In dual-coded VA systems (described in Section \ref{methods-data}), two physicians are randomly assigned to each record and require second inspections of each other's assignment (reconciliation) and evaluation by a third more senior physician if their assignments do not agree. As mentioned in Section \ref{discuss-adv-hscav}, suggestion of alternative assignments from GPT and InSilicoVA models potentially reduces the disagreement between physicians, and ill-defined records, while allowing physicians to focus on more difficult records. Thus, model suggestions can be integrated into VA systems by presenting COD suggestions to physicians after their initial COD assignment, which allows them to consider alternative assignments and possibly revise their assignments based on the suggestions. At step 2 in Figure \ref{fig-discuss-phyassist}, GPT, InterVA-5, and InSilicoVA models can suggest COD assignments to consider, providing the option in step 2b to revise or proceed with their initial assignment. Our future work will be a first step in computer assisted verbal autopsy, assessing the effects of these model suggestions on improve VA data quality (e.g. increase in agreed records, reduction of ill-defined deaths). In preparation, we have integrated GPT-4, InterVA-5, and InSilicoVA model suggestions into our on-going HEAL-SL study after survey round 2 \citep{njalauniversityHealthySierraLeone2023} with goals of increasing physician agreement and reducing ill-defined COD assignments.

@@

CSMF accuracy measures the performance of models at the population level, comparing distributions of CODs between the physicians and the models \citep{murrayRobustMetricsAssessing2011}. To calculate CSMF accuracy, we first calculate $CSMF_j$ as is the fraction of physician or model records for cause $j$, given by dividing the number of records for cause $j$ with the total number of records as seen in Equation \ref{eq-csmf}. Then, the $CSMFMaximumError$, representing the worst possible model, is calculated using Equation \ref{eq-csmferr}. Finally, the CSMF accuracy is given by Equation \ref{eq-csmfa}, where $k$ is the number of causes, $j$ is a cause, $CSMF^{true}_j$ is the true physician CSMF for cause $j$, and $CSMF^{pred}_j$ is the prediction model CSMF for cause $j$. CSMF accuracy ranges from 0 to 1, where 1 means that the model completely matched the physician COD distribution and 0 means that it did not match the distribution at all.

@@

PCCC measures the performance of models at the individual level, comparing COD assignments between the physicians and models on a record by record basis, correcting for COD assignments made purely by chance \citep{murrayRobustMetricsAssessing2011}. PCCC is given by Equation \ref{eq-pccc}, where $k$ is the number of top COD assignments from the model to consider, $N$ is number of causes, and $C$ is fraction of records where the physician COD assignment is one of the top COD assignments from the model. For this study, we set $k$ to 1, making $C$ equivalent to the fraction of true positives $TP$ or records where the physician COD assignment is equal to the model COD assignment as shown in Equation \ref{eq-pccc-c}. Higher PCCC values closer to 1 indicate that model COD assignments are similar to physician COD assignments, while values closer to 0 indicate that model COD assignments are not similar to physicians.

>>>>

Recently, Large Language Models (LLM), leveraging massive datasets and deep learning approaches, have made advances in performing a variety of Natural Language Processing (NLP) tasks using free-text, such as question answering, code generation, and even medical diagnosis \citep{changSurveyEvaluationLarge2023,lundChattingChatGPTHow2023,svyatkovskiyIntelliCodeComposeCode2020,hauptAIGeneratedMedicalAdvice2023}. In 2022, a widely-available LLM called ChatGPT was released by OpenAI with capabilities of answering natural language text inquiries using training data up to September 2021. ChatGPT-3 was based on several Generative Pre-trained Transformer (GPT) models between 2018 to 2020, namely GPT-1 to GPT-3, which had notable differences in training data sizes of 5 gigabytes to 45 terabytes from web sources that resulted in 117 million to 175 billion parameter models \citep{wuBriefOverviewChatGPT2023}. In March 2023, ChatGPT-4 was released with human-level performance on various professional and academic exams and benchmarks that outperformed ChatGPT-3 \citep{openaiGPT4TechnicalReport2023}. Given the limited usage of free-text open narratives in computer models for determining CODs, and recent advances in LLMs that leverage natural language text prompts, a study was conducted for Sierra Leone deaths from VA in 2019 to 2022 to compare four models, GPT-3.5, GPT-4, InterVA-5, and InSilicoVA, to physicians for determining CODs.

@@

Since computer models were compared to physicians in this study, there was more certainty that COD assignments agreed by both physicians were representative of physician assignment than when they disagreed \citep{barnettComparativeAccuracyDiagnosis2019,morrisFactorsAssociatedPhysician2010,hsiaoFactorsAssociatedPhysician2012}. Thus, 6942 physician agreed records of the 11,920 total records were used. For better comparison, all codes were standardized to CGHR-10 codes (see Additional File 1) that generalized ICD-10 codes into 19, 10, and 7 categories for the adult (12 to 69 years), child (28 days to 11 years), and neonatal (under 28 days) age groups. After conversion, a final total of 6939 physician agreed records (3826 adult, 2636 child, and 477 neonatal) were used for modelling and performance evaluation. See Appendix \ref{app-methods-data} for further details on data preprocessing and Tables \ref{tab-data-cod} and \ref{tab-data-age} for COD and age range distributions of the physician agreed records.

@@

Of all 6939 records, GPT-4 (0.61 PCCC) had the highest individual performance followed by GPT-3.5 (0.56 PCCC), InSilicoVA (0.44 PCCC), and InterVA-5 (0.44 PCCC) (Figure \ref{fig-pccc-csmf}). GPT-3.5 and GPT-4 had improvements ranging from 0.14-0.18 PCCC over InSilicoVA and InterVA-5, while GPT-4 slightly improved over GPT-3.5 by 0.05 PCCC. Population level performances were similar for all models (0.74-0.79 CSMF). Figure \ref{fig-pccc} shows the PCCC performance across three age groups (adult, child, and neonate). GPT-4 had the best individual performance for adult and neonatal records (0.64 and 0.58 PCCC), while GPT-3.5 had the best performance for child records (0.54 PCCC) with GPT-4 performing slightly worse (0.51 PCCC). InSilicoVA and InterVA-5 performed the worse for adult and child records ($\leq$0.5 PCCC), while GPT-3.5 performed the worse for neonatal records (0.42 PCCC). Across ages, all models followed a similar pattern in individual performance (Figure \ref{fig-pccc-age}). PCCC trended upwards for 1 month to 14 years ($\sim$0.1-0.75), and downwards for ages 15 to 69 years ($\sim$0.7-0.35). The highest and lowest performances were observed for ages 12-29 years ($\sim$0.4-0.7) and 1-11 months ($\sim$0.1-0.35) respectively. Performances varied more across models for ages 0 days to 5 years, while varying less from 5 to 69 years between GPT-3.5 and GPT-4, and between InSilicoVA and InterVA-5.

@@

GPT-3.5 and GPT-4 models used default parameters with the exception of setting the temperature to 0 for more consistent results. However, the temperature and other model settings may be adjusted to possibly improve performance for GPT models \citep{openaiOpenAIPlatformAPI2024}. This was not examined as sensitivity analyses on model parameters are costly across multiple reruns, noted in Section \ref{discuss-disadv-reprod}, which is required when testing various parameter settings. In addition, GPT models may possibly produce inconsistent results even with the temperature set to 0. Thus, it is important to also test the reliability and consistency of GPT outputs to avoid coincidental results due to randomness \citep{johnsonAssessingAccuracyReliability2023,jangConsistencyAnalysisChatGPT2023,krishnaEvaluationReliabilityRepeatability2024}. InterVA-5 and InSilicoVA were able to provide multiple COD assignments with probabilities for each COD. GPT models can be prompted to produce more than one COD assignment, but was not explored in this study as only most probable COD was evaluated. This may be useful to evaluate the performance of multiple alternative COD assignments, which may provide additional diagnoses that have a higher chance of being similar to physician assignment, and better reflect causes leading to death \citep{solemanVerbalAutopsyCurrent2006}.

@@

Our study lays the foundation for the integration of GPT, InterVA-5, and InSilicoVA models into VA systems to assist physicians in COD assignment. In dual-coded VA systems (described in Section \ref{methods-data}), two physicians are randomly assigned to each record and require second inspections of each other's assignment (reconciliation) and evaluation by a third more senior physician if their assignments do not agree. As mentioned in Section \ref{discuss-adv-hscav}, suggestion of alternative assignments from GPT and InSilicoVA models potentially reduces the disagreement between physicians, and ill-defined records, while allowing physicians to focus on more difficult records. Thus, model suggestions can be integrated into VA systems by presenting COD suggestions to physicians after their initial COD assignment, which allows them to consider alternative assignments and possibly revise their assignments based on the suggestions. At step 2 in Figure \ref{fig-discuss-phyassist}, GPT, InterVA-5, and InSilicoVA models can suggest COD assignments to consider, providing the option in step 2b to revise or proceed with their initial assignment. Our future work will be a first step in computer assisted verbal autopsy, assessing the effects of these model suggestions on improve VA data quality (e.g. increase in agreed records, reduction of ill-defined deaths). In preparation, GPT-4, InterVA-5, and InSilicoVA model suggestions have been integrated into the on-going HEAL-SL study after survey round 2 \citep{njalauniversityHealthySierraLeone2023} with goals of increasing physician agreement and reducing ill-defined COD assignments.

@@

CSMF accuracy measures the performance of models at the population level, comparing distributions of CODs between the physicians and the models \citep{murrayRobustMetricsAssessing2011}. To calculate CSMF accuracy, $CSMF_j$ was calculated as is the fraction of physician or model records for cause $j$, given by dividing the number of records for cause $j$ with the total number of records as seen in Equation \ref{eq-csmf}. Then, the $CSMFMaximumError$, representing the worst possible model, is calculated using Equation \ref{eq-csmferr}. Finally, the CSMF accuracy is given by Equation \ref{eq-csmfa}, where $k$ is the number of causes, $j$ is a cause, $CSMF^{true}_j$ is the true physician CSMF for cause $j$, and $CSMF^{pred}_j$ is the prediction model CSMF for cause $j$. CSMF accuracy ranges from 0 to 1, where 1 means that the model completely matched the physician COD distribution and 0 means that it did not match the distribution at all.

@@

PCCC measures the performance of models at the individual level, comparing COD assignments between the physicians and models on a record by record basis, correcting for COD assignments made purely by chance \citep{murrayRobustMetricsAssessing2011}. PCCC is given by Equation \ref{eq-pccc}, where $k$ is the number of top COD assignments from the model to consider, $N$ is number of causes, and $C$ is fraction of records where the physician COD assignment is one of the top COD assignments from the model. For this study, $k$ was set to 1, making $C$ equivalent to the fraction of true positives $TP$ or records where the physician COD assignment is equal to the model COD assignment as shown in Equation \ref{eq-pccc-c}. Higher PCCC values closer to 1 indicate that model COD assignments are similar to physician COD assignments, while values closer to 0 indicate that model COD assignments are not similar to physicians.

### 2025-06-18 src/plots.Rmd
Remove we

# Plot performance of models using lines and points
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        color = "model_name",
        text_scale = 1,
        title = NULL,
        title_size = 10,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2.25 * text_scale,
        text_mid_vjust = 2.5,
        text_start_size = 3 * text_scale,
        text_end_size = 4 * text_scale,
        text_hjust = 0.2,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 2.5,
        min_points_size = 2,
        max_points_size = 3,
        x_limits = c(0, 1),
        x_breaks = seq(0, 1, by = 0.1),
        x_expand = expansion(add = 0.2),
        x_color_labels = c(
            "G3" = "GPT-3.5 (G3)",
            "G4" = "GPT-4 (G4)",
            "ISV" = "InSilicoVA (ISV)",
            "I5" = "InterVA-5 (I5)"
        ),
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        sort_group = T,
        legend_position = "bottom",
        legend_title = element_blank(),
        legend_margin = margin(c(-8, -2, -2, -2)),
        ...
    ) {

@@

    # Plot trend lines for each model
    out <- ggplot(
        df_plot,
        aes(
            x = .data[[group]],
            y = metric,
            color = model_name,
            group = model_name
        )
    ) +
        geom_line(linewidth = 0.75, alpha = 0.4) + 
        geom_line(
            data = df_plot %>%
                group_by(.data[[group]]) %>%
                summarize(
                    metric = mean(metric),
                    model_name = "Mean Across Models"
                ),
            aes(color = model_name),
            se = F,
            linewidth = 1.25
        ) +
        scale_color_manual(values = default_colors, labels = x_color_labels) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.title = element_blank(),
            legend.text = element_text(size = legend_text_size),
            legend.position = legend_position, 
            legend.direction = legend_direction,
            legend.box.spacing = legend_spacing,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )
    return(out)

@@

# Plot data
fig_pccc_csmf <- ggplot(
    df_plot,
    aes(
        x = metric_value,
        y = model_name,
        fill = metric
    )
) +
    geom_bar(
        stat = "identity",
        position = position_dodge(),
        color = "black",
        width = 0.7
    ) +
    geom_text(
        data = df_plot,
        aes(
            label = round(metric_value, 2)
        ),
        position = position_dodge(width = 0.7),
        color = "black",
        fill = "white",
        size = 3,
        label.r = unit(0, "pt"),
        vjust = 0.5,
        hjust = -0.25
    ) +
    scale_x_continuous(
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
    ) +
    labs(
        title = NULL,
        x = NULL,
        y = NULL
    ) +
    theme_minimal() +
    theme(
        # panel.border = element_rect(
        #     color = "black",
        #     fill = NA,
        #     linewidth = 0.75
        # ),
        legend.position = c(.875, .5),
        legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8)
    )

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC)",
    text_mid_vjust = -1,
    text_scale = 1
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-adult.pdf",
    fig_pccc_cod_adult,
    width = 170,
    height = 225,
    units = "mm",
    dpi = 300
)

>>>>

# Plot performance of models using lines and points
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        color = "model_name",
        text_scale = 1,
        title = NULL,
        title_size = 10,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2.25 * text_scale,
        text_mid_vjust = 2.5,
        text_start_size = 3 * text_scale,
        text_end_size = 4 * text_scale,
        text_hjust = 0.2,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 4,
        min_points_size = 4,
        max_points_size = 4,
        x_limits = c(0, 1),
        x_breaks = seq(0, 1, by = 0.1),
        x_expand = expansion(add = 0.2),
        x_color_labels = c(
            "G3" = "GPT-3.5 (G3)",
            "G4" = "GPT-4 (G4)",
            "ISV" = "InSilicoVA (ISV)",
            "I5" = "InterVA-5 (I5)"
        ),
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        sort_group = T,
        legend_position = "bottom",
        legend_title = element_blank(),
        legend_margin = margin(c(-8, -2, -2, -2)),
        ...
    ) {

@@

    # Plot trend lines for each model
    out <- ggplot(
        df_plot,
        aes(
            x = .data[[group]],
            y = metric,
            color = model_name,
            group = model_name
        )
    ) +
        geom_line(linewidth = 1.15, alpha = 0.5) + 
        geom_line(
            data = df_plot %>%
                group_by(.data[[group]]) %>%
                summarize(
                    metric = mean(metric),
                    model_name = "Mean Across Models"
                ),
            aes(color = model_name),
            se = F,
            linewidth = 1.5
        ) +
        scale_color_manual(values = default_colors, labels = x_color_labels) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.title = element_blank(),
            legend.text = element_text(size = legend_text_size),
            legend.position = legend_position, 
            legend.direction = legend_direction,
            legend.box.spacing = legend_spacing,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )
    return(out)

@@

# Plot data
fig_pccc_csmf <- ggplot(
    df_plot,
    aes(
        x = metric_value,
        y = model_name,
        fill = metric
    )
) +
    geom_bar(
        stat = "identity",
        position = position_dodge(),
        color = "black",
        width = 0.7
    ) +
    geom_text(
        data = df_plot,
        aes(
            label = round(metric_value, 2)
        ),
        position = position_dodge(width = 0.7),
        color = "black",
        fill = "white",
        size = 4.5,
        label.r = unit(0, "pt"),
        vjust = 0.5,
        hjust = -0.25
    ) +
    scale_x_continuous(
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
    ) +
    labs(
        title = NULL,
        x = NULL,
        y = NULL
    ) +
    theme_minimal() +
    theme(
        # panel.border = element_rect(
        #     color = "black",
        #     fill = NA,
        #     linewidth = 0.75
        # ),
        legend.position = c(.875, .45),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)
    )

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC)",
    text_mid_vjust = 2,
    text_scale = 1.25
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-adult.pdf",
    fig_pccc_cod_adult,
    width = 170,
    height = 250,
    units = "mm",
    dpi = 300
)
